*flippant* --- An R package for the automated analysis of dithionite scramblase

### 2016-06-16 inst/manuscript/manuscript.rmd
Reformat code chuncks in manuscript;

```{r noeval_template_generation_call, code=formatR::usage('scramblase_assay_input_template'), eval=FALSE}
```

@@

```{r noeval_traces_call, code = formatR::usage('scramblase_assay_traces'), eval = FALSE}
```

@@

```{r noeval_plot_call, code = formatR::usage('scramblase_assay_plot'), eval = FALSE}
```

@@

```{r noeval_stats_call, code = formatR::usage('scramblase_assay_stats'), eval = FALSE}
```

@@

```{r noeval_demonstrate_traces, eval = FALSE}
# Plot spectral traces (Figure 1A)
scramblase_assay_traces("inputTable.txt", time_max_sec = 350)
```

```{r figure1_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*--based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblase_assay_traces`, while (B) and (C) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 2 (see text for details). In (B) data is separately plotted for independent experiments, while (C) combines all data points, aiming for reliability of fit. 'adj. PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
x <- flippant:::read_scramblase_input_file(
  file.path(tmpDir,"inputTable.txt"))
x[["Path"]] <- file.path(tmpDir, x[["Path"]])
figure1 <- add_panel(
  figure = figure1,
  top_panel = 1,
  bottom_panel = 3,
  left_panel = 1, 
  right_panel = 3, 
  panel = scramblase_assay_traces(x, time_max_sec = 350) + theme_bw())
figure1 <- add_panel(
  figure = figure1,
  top_panel = 4,
  bottom_panel = 5,
  left_panel = 1, 
  right_panel = 3, 
  panel = scramblase_assay_plot(x, generation_of_algorithm = 2) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
figure1 <- add_panel(
  figure = figure1,
  top_panel = 6,
  bottom_panel = 7,
  left_panel = 1,
  right_panel = 3,
  panel = scramblase_assay_plot(x, generation_of_algorithm = 2, split_by_experiment = FALSE) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])) +
    facet_wrap(c("`Experimental Series`"))+
    guides(colour = "none"))
grid.draw(figure1)
```

@@

```{r noeval_demonstrate_plot, eval = FALSE}
# Plot PPR plot (Figure 1B)
scramblase_assay_plot("inputTable.txt", generation_of_algorithm = 2) + xlim(0, 2)
```

@@

```{r noeval_demonstrate_plot2, eval = FALSE}
# Plot PPR plot (Figure 1C)
scramblase_assay_plot("inputTable.txt",
  generation_of_algorithm = 2,
  split_by_experiment = FALSE) + 
xlim(0, 2)
```

@@

```{r noeval_demonstrate_tabular_writeout, eval = FALSE}
# Write out results in tabular manner (Table 1)
scramblase_assay_stats("inputTable.txt", generation_of_algorithm = 2, split_by_experiment = FALSE)
```

>>>>

```{r noeval_template_generation_call, code=formatR::usage('scramblase_assay_input_template', width = 60), eval=FALSE}
```

@@

```{r noeval_traces_call, code = formatR::usage('scramblase_assay_traces', width = 60), eval = FALSE}
```

@@

```{r noeval_plot_call, code = formatR::usage('scramblase_assay_plot', width = 65), eval = FALSE}
```

@@

```{r noeval_stats_call, code = formatR::usage('scramblase_assay_stats', width = 65), eval = FALSE}
```

@@

```{r noeval_demonstrate_traces, eval = FALSE}
# Plot spectral traces (Figure 1A)
scramblase_assay_traces(
  "inputTable.txt",
  time_max_sec = 350)
```

```{r figure1_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*--based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblase_assay_traces`, while (B) and (C) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 2 (see text for details). In (B) data is separately plotted for independent experiments, while (C) combines all data points, aiming for reliability of fit. 'adj. PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
x <- tmpDir %>%
  file.path("inputTable.txt") %>%
  flippant:::read_scramblase_input_file()
x[["Path"]] <- file.path(tmpDir, x[["Path"]])
figure1 <- add_panel(
  figure = figure1,
  top_panel = 1,
  bottom_panel = 3,
  left_panel = 1, 
  right_panel = 3, 
  panel = scramblase_assay_traces(x, time_max_sec = 350) + theme_bw())
figure1 <- add_panel(
  figure = figure1,
  top_panel = 4,
  bottom_panel = 5,
  left_panel = 1, 
  right_panel = 3, 
  panel = scramblase_assay_plot(x, generation_of_algorithm = 2) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])))
figure1 <- add_panel(
  figure = figure1,
  top_panel = 6,
  bottom_panel = 7,
  left_panel = 1,
  right_panel = 3,
  panel = scramblase_assay_plot(x, generation_of_algorithm = 2, split_by_experiment = FALSE) + 
    theme_bw() + 
    xlim(0, 2) + 
    xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ylab(expression(P[{phantom()>=1}])) +
    facet_wrap(c("`Experimental Series`"))+
    guides(colour = "none"))
grid.draw(figure1)
```

@@

```{r noeval_demonstrate_plot, eval = FALSE}
# Plot PPR plot (Figure 1B)
scramblase_assay_plot(
  "inputTable.txt",
  generation_of_algorithm = 2) +
xlim(0, 2)
```

@@

```{r noeval_demonstrate_plot2, eval = FALSE}
# Plot PPR plot (Figure 1C)
scramblase_assay_plot(
  "inputTable.txt",
  generation_of_algorithm = 2,
  split_by_experiment = FALSE) + 
xlim(0, 2)
```

@@

```{r noeval_demonstrate_tabular_writeout, eval = FALSE}
# Write out results in tabular manner (Table 1)
scramblase_assay_stats(
  "inputTable.txt",
  generation_of_algorithm = 2,
  split_by_experiment = FALSE)
```
